### 2017-11-06 1/exams/m2.tex
m2 draft.

\begin{center}
\begin{tabular}{| c | c |}
  \hline
  Question & Points \\ \hline \hline
  1 & 12 \\ \hline
  2 & 12 \\ \hline
  3 & 15 \\ \hline
  4 & 15 \\ \hline
  5 & 15 \\ \hline
  6 & 10 \\ \hline
  7 & 15 \\ \hline \hline
  Total: & 94\\
  \hline
\end{tabular}
\end{center}

@@

\noindent
{\bf Problem 1 (12 points).}
%
Each of the following signatures describes a class of functions:

\begin{verbatim}
Boolean String -> String
[Boolean -> String] -> String
[Listof Boolean] [Listof Number] -> Number
[X] . [Number -> X] -> X
[X Y] . [X -> Y] [Listof X] -> [Listof Y]
[X Y Z] . [X -> Y] [Y -> Z] X -> Z
\end{verbatim}
Define one example of a function in each class.  (You only need to
provide the code, not a full design.)

@@

\noindent
{\bf Problem 3 (15 points).}
%
Design a program called {\tt w-avg} that computes the weighted average
of a list of numbers and a list of weights.

@@

\noindent
{\bf Problem 6 (10 points).}
%
It's been said that {\tt foldr} is \emph{the} fundamental list
abstraction function because any function that follows the list
template can be expressed in terms of {\tt foldr}.  Put that theory to
the test by providing an equivalent definition for the following
function in terms of {\tt foldr}:

\begin{verbatim}
;; map : [X Y] . [X -> Y] [Listof X] -> [Listof Y]
;; Apply f to each element of list, collect a list of results
(define (map f ls)
  (cond [(empty? ls) '()]
        [(cons? ls)
         (cons (f (first ls))
               (map f (rest ls)))]))
\end{verbatim}

\noindent
(Just provide code, not a full design.)

(define (map f xs)
  (foldr (lambda (x ys) (cons (f x) ys)) '() xs))
\end{SaveVerbatim}

\noindent
{\bf Problem 7 (15 points).}
%
Here's a data definition for choose-your-own-adventure books:
\begin{verbatim}
;; A CYOA is one:
;; - String
;; - (make-choice String CYOA CYOA)
(define-struct choice (q yes no))
;; Interp: a choose-your-own-adventure book where a string
;; is a conclusion and a choice is a yes/no question and
;; the two adventures that follow as a consequnce of the answer.
\end{verbatim}

@@

;; most-games : Tournament -> Number
;; Compute most games any team has to win to win tournament
(check-expect (most-games "NY") 0)
(check-expect (most-games (make-bracket "LA" "HOU")) 1)
(check-expect (most-games (make-bracket (make-bracket "LA" "DC") "HOU")) 2)
(define (most-games t)
  (cond [(string? t) 0]
        [(bracket? t)
         (add1 (max (most-games (bracket-t1 t))
                    (most-games (bracket-t2 t))))]))
\end{SaveVerbatim}

>>>>

\begin{center}
\begin{tabular}{| c | c |}
  \hline
  Question & Points \\ \hline \hline
  1 & 15 \\ \hline
  2 & 12 \\ \hline
  3 & 20 \\ \hline
  4 & 20 \\ \hline
  5 & 15 \\ \hline
  6 & 20 \\ \hline\hline
  Total: & 102\\
  \hline
\end{tabular}
\end{center}

@@

\noindent
{\bf Problem 1 (15 points).}
%
Here are some data definition relevant to representing a dictionary,
which associates words with the their definitions:

\begin{verbatim}
;; A Dict is one of:
;; - '()
;; - (cons (list String String) Dict)
;; Interp: represents a collection of definitions where each
;; element is a two-element list consisting of a word (first) and its
;; meaning (second).

;; A Result is one of:
;; - #false
;; - String
;; Interp: represents the result of looking up a word in the
;; dictionary; #false means not found.
\end{verbatim}

\noindent
Design the following function:

\begin{verbatim}
;; lookup : String Dict -> Result
;; Lookup the (first) definition of a word in the dictionary,
;; produces #false if not found
\end{verbatim}

@@

\noindent
{\bf Problem 3 (20 points).}
%
Design a program called {\tt w-avg} that computes the weighted average
of a list of numbers and a list of weights.

@@

\noindent
{\bf Problem 6 (20 points).}
%
Here's a data definition for choose-your-own-adventure books:
\begin{verbatim}
;; A CYOA is one:
;; - String
;; - (make-choice String CYOA CYOA)
(define-struct choice (q yes no))
;; Interp: a choose-your-own-adventure book where a string
;; is a conclusion and a choice is a yes/no question and
;; the two adventures that follow as a consequnce of the answer.
\end{verbatim}

@@

(define a0 "A0")
(define a1 (make-choice "Q1" "A1" "A2"))
(define a2 (make-choice "Q2" a0 a1))

;; ans : CYOA [Listof Boolean] -> CYOA
;; ...
(check-expect (adv a0 (list #true #false)) "A0")
(check-expect (adv a1 (list #true #false)) "A1")
(check-expect (adv a2 (list #false #true)) "A1")
(check-expect (adv a2 (list #false)) a1)
(define (ans adv loa)
  (cond [(string? adv) adv]
        [(empty? loa) adv]
        [(first loa)
         (ans (choice-yes adv) (rest adv))]
        [else
         (ans (choice-no adv) (rest adv))]))
\end{SaveVerbatim}
